\textbf{International Transport costs:\\New Findings from modeling additive costs}\\Online Appendix (Not for Publication)

### 2021-10-26 redaction/JEGeo/revision_JEGeo/revised_article/DHP_JoEG_rev1.tex
modifs textes

\begin{table}[htbp]
	\centering
	\caption{Robustness to the separability assumption - restricted sample}
	\begin{center}
			\input{Table4_reshaped.tex}
			\input{Table4.tex}
	\end{center}
	\parbox[l]{12cm}{\footnotesize{Notes: Estimations are performed on a restricted sample, based on the following rule:  we select, for each year, the largest importers that form together at least 80\% of annual trade and the largest traded sectors that form together at least 80\% of annual trade. We keep in the sample all trade observations from these importers and in these sectors.
			The additive term is expressed in fraction of fas price.}}
	\label{tab:robustness_separability}
\end{table}

Three main comments can be made. First, the subset of large trade flows we are considering (around 8\% of the observations of our initial sample, but the vast majority of the total value of aggregated trade (an annual mean of 68\% )
%use "/Users/guillaumedaudin/Documents/Recherche/2013 -- Trade Costs -- local/results/comparaisons_various/stats_comp_baseline_non_séparé.dta", clear
%gen cover = cover_non_séparé/cover_baseline
%sum coveruse "/Users/guillaumedaudin/Documents/Recherche/2013 -- Trade Costs -- local/results/comparaisons_various/stats_comp_baseline_non_séparé.dta", clear
%gen cover = cover_non_séparé/cover_baseline
%sum cover
involve a higher share of additive costs: between 48\% and 55\% of total costs on average, versus 30\% to 44\% on the whole sample.
%JH: la phrase suivante est en contradiction avec celle qui suit encore juste après: "Second, assuming that country/product fixed effects are separable in these two dimensions tends to overestimate the value and the share of the additive costs."
Second, both models provide a similar quality of fit of the regression (once we take into account the number of right-hand-side variables) as the AIC criteria display very close values in both models (conditional on transport mode). Third, the estimated values remain of similar magnitude under both separability and non-separability assumptions.\footnote{We also run two other robustness checks: \textit{i}) comparing the results on a detailed yearly basis and \textit{ii}) reporting the histogram of the distribution for $\beta$ over the triple $(i,k,t)$, which confirm the robustness of the results. These results are reported in the Online Appendix, \textbf{Section XXX} for sake of space saving.} %, even if one can note that under the separability assumption, the share of additive costs seems slightly biased upward, at least for averages over the period. The picture is reversed for medians

>>>>

\begin{table}[htbp]
	\centering
	\caption{Robustness to the separability assumption - restricted sample}
	\begin{center}
			\input{Table4_reshaped.tex}
%			\input{Table4.tex}
	\end{center}
	\parbox[l]{12cm}{\footnotesize{Notes: Estimations are performed on a restricted sample, based on the following rule:  we select, for each year, the largest importers that form together at least 80\% of annual trade and the largest traded sectors that form together at least 80\% of annual trade. We keep in the sample all trade observations from these importers and in these sectors.
			The additive term is expressed in fraction of fas price.}}
	\label{tab:robustness_separability}
\end{table}

Three main comments can be made. First, the subset of large trade flows we are considering (around 8\% of the observations of our initial sample, but the vast majority of the total value of aggregated trade (an annual mean of 68\% XXX D'OU VIENT CE CHIFFRE DE 68\% ?? N'est-ce pas 80\% ???).
%use "/Users/guillaumedaudin/Documents/Recherche/2013 -- Trade Costs -- local/results/comparaisons_various/stats_comp_baseline_non_séparé.dta", clear
%gen cover = cover_non_séparé/cover_baseline
%sum coveruse "/Users/guillaumedaudin/Documents/Recherche/2013 -- Trade Costs -- local/results/comparaisons_various/stats_comp_baseline_non_séparé.dta", clear
%gen cover = cover_non_séparé/cover_baseline
%sum cover
involve a higher share of additive costs: between 48\% and 55\% of total costs on average, versus 30\% to 44\% on the whole sample.
%JH: la phrase suivante est en contradiction avec celle qui suit encore juste après: "Second, assuming that country/product fixed effects are separable in these two dimensions tends to overestimate the value and the share of the additive costs."
Second, both models provide a similar quality of fit of the regression (once we take into account the number of right-hand-side variables) as the AIC criteria display very close values in both models (conditional on transport mode). Third, the estimated values remain of similar magnitude under both separability and non-separability assumptions.\footnote{We also run two other robustness checks: \textit{i}) comparing the results on a detailed yearly basis and \textit{ii}) reporting the histogram of the distribution for $\beta$ over the triplet $(i,k,t)$, which confirm the robustness of the results. These results are reported in the Online Appendix, respectively in sections C and D.2.} %, even if one can note that under the separability assumption, the share of additive costs seems slightly biased upward, at least for averages over the period. The picture is reversed for medians
